---
title: "Activity: Street or Road?"
author: "Edward Cho"
output: html_notebook
---

## Load in the data

```{r}
#load libraries

library(tidyverse)

#load in the data here

download.file( url = "https://mdbeckman.github.io/dcSupplement/data/street-addresses.csv", destfile = "street-addresses.csv")
DataTable1 <- read.csv("street-addresses.csv")
download.file( url = "https://mdbeckman.github.io/dcSupplement/data/CMS_ProvidersSimple.rds", destfile = "CMSProvidersSimple.rds")
DataTable2 <- readRDS("CMSProvidersSimple.rds")

# we will only be using the "street-addresses.csv" file from the text



```

## Recreate Solved Example using `sample(50)`

```{r}
Addresses <- read_csv("https://mdbeckman.github.io/dcSupplement/data/street-addresses.csv")
Sample <- 
  Addresses %>%
  sample_n(size = 50)

```

## Recreate Solved Example using the entire `Address` data set

```{r}
pattern <- "BOX\\s+(\\d+)"

BoxNumbers <- 
  Addresses %>%
  filter(grepl(pattern, address)) %>%
  tidyr::extract(address, into = "boxnum", regex = pattern)
```

#### Additional Question: How many addresses are a PO BOX (including NCSU BOX)? 

```{r}
BoxNumbers %>%
  summarise( Cases = n())

```

My answer here...... 


## Back to the Streets: Your Turn

#### Part 1: Explain (in english) each line of the following code chunk

```{r}
pattern <- "(ST|RD|ROAD)"
LeftOvers <-
  Addresses %>% 
  filter( !grepl(pattern, address),
          !grepl("\\sAPT|UNIT\\s[\\d]+$", address),
          !grepl(" BOX ", address)
          )
```

My answer here.......

#### Part 2: Implement your method on the entire `Addresses` data set. Explain how your code works line by line.

```{r}



```

My answer here.......

#### Additional Question 1: Present your result from part 2 by providing a table in descending order of popularity for the street name endings you found

```{r}


```

#### Additional Question 2: Present your result by using ggplot to a bar chart in descending order of popularity for the street name endings you found previously.

Note: make sure your order street names according to popularity, not alphabetically.

```{r}

```

#### Additional Question 3: Comment on any patterns you see

My answer here.......
